Child Poverty Interventions

### 2023-10-05 minos/outcomes/child_poverty_reduction_vis.Rmd

```{r, include=FALSE}
out.path <- here::here('output', 'default_config/')
base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
int.dat <- read_singular_local_out(out.path, 'ChildPovertyReduction', drop.dead = TRUE)
#base.dat <- read_agg_subset_batch_out(out.path, 'baseline', drop.dead = TRUE)
#int1.dat <- read_agg_subset_batch_out(out.path, 'ChildPovertyReduction', drop.dead = TRUE)
```

@@

The first intervention we will focus on is a reduction in the prevalence of children in relative poverty.

@@

## Boosted Sample

@@

```{r}
hh_boosted <- int.dat %>%
  select(hidp, time, income_boosted, boost_amount, nkids) %>%
  filter(income_boosted == 'True') %>%
  group_by(time) %>%
  summarise(n_boosted = length(unique(hidp)),
            total_boost = sum(boost_amount),
            kids_boosted = sum(nkids))

ggplot(hh_boosted, aes(x = time, y = n_boosted)) +
  geom_line() +
  geom_vline(xintercept = 2030, linetype = 'dashed') +
  labs(title = 'Number of households receiving intervention') +
  xlab('Year') +
  ylab('Number Boosted')

ggplot(hh_boosted, aes(x = time, y = kids_boosted)) +
  geom_line() +
  geom_vline(xintercept = 2030, linetype = 'dashed') +
  labs(title = 'Number of children in households receiving intervention') +
  xlab('Year') +
  ylab('Number Children')

ggplot(hh_boosted, aes(x = time, y = total_boost)) +
  geom_line() +
  geom_vline(xintercept = 2030, linetype = 'dashed') +
  labs(title = 'Total boost amount') +
  xlab('Year') +
  ylab('Boost Amount')

@@

ggplot(mean.boost, aes(x = time, y = mean_boost)) +
  geom_line() +
  geom_vline(xintercept = 2030, linetype = 'dashed') +
  labs(title = 'Mean boost amount') +
  xlab('Year') +
  ylab('Boost Amount')
```

@@

## SF_12_MCS

@@

### Full Sample

@@

```{r}
base.all.SF12 <- base.dat %>%
  select(time, weight, SF_12) %>%
  group_by(time) %>%
  summarise(base.SF12 = weighted.mean(SF_12, w = weight))

@@

ggplot(combined, aes(x = time, y = diff)) +
  geom_line() +
  geom_hline(yintercept = 0, linetype='dashed') +
  labs(title = 'Relative change in SF12') +
  xlab('Year') +
  ylab('Difference')
```

### Families with children

@@

```{r}
base.all.SF12 <- base.dat %>%
  select(time, weight, SF_12, nkids) %>%
  filter(nkids > 0) %>%
  group_by(time) %>%
  summarise(base.SF12 = weighted.mean(SF_12, w = weight))

@@

ggplot(combined, aes(x = time, y = diff)) +
  geom_line() +
  geom_hline(yintercept = 0, linetype='dashed') +
  labs(title = 'Relative change in SF12') +
  xlab('Year') +
  ylab('Difference')
```

### Families w/ children under poverty line

@@

```{r}
base.thresh <- merge(base.dat, threshold, by = 'time')
int.thresh <- merge(int.dat, threshold, by = 'time')

@@

ggplot(combined, aes(x = time, y = diff)) +
  geom_line() +
  geom_hline(yintercept = 0, linetype='dashed') +
  labs(title = 'Relative change in SF12') +
  xlab('Year') +
  ylab('Difference')
```

@@

### Treatment on the Treated

```{r}
boosted.overtime <- int.dat %>%
  filter(income_boosted == 'True')

base.all.SF12 <- base.dat %>%
  select(time, weight, SF_12, nkids, pidp) %>%
  filter(pidp %in% boosted.overtime$pidp) %>%
  group_by(time) %>%
  summarise(base.SF12 = weighted.mean(SF_12, w = weight))

int.all.SF12 <- int.dat %>%
  select(time, weight, SF_12, nkids, pidp) %>%
  filter(pidp %in% boosted.overtime$pidp) %>%
  group_by(time) %>%
  summarise(int.SF12 = weighted.mean(SF_12, w = weight))

@@

ggplot(combined, aes(x = time, y = diff)) +
  geom_line() +
  geom_hline(yintercept = 0, linetype='dashed') +
  labs(title = 'Relative change in SF12') +
  xlab('Year') +
  ylab('Difference')
```

>>>>

```{r, include=FALSE}
out.path <- here::here('output', 'default_config/')
base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
int.dat <- read_singular_local_out(out.path, 'ChildPovertyReductionRANDOM', drop.dead = TRUE)
int2.dat <- read_singular_local_out(out.path, 'ChildPovertyReductionSUSTAIN', drop.dead = TRUE)
#base.dat <- read_agg_subset_batch_out(out.path, 'baseline', drop.dead = TRUE)
#int1.dat <- read_agg_subset_batch_out(out.path, 'ChildPovertyReduction', drop.dead = TRUE)
```

@@

The first intervention we will focus on is a reduction in the prevalence of children in relative poverty. In these interventions, we have a target level of child poverty to attain (10% of children in a household in poverty) by a specified target year, which is 2030 unless stated otherwise. To achieve this, we find households with a hh_income under the poverty line, and uplift a number of households each year to linearly achieve the target proportion by the target year.

@@

## Random Uplift

In this intervention, we will randomly select households to uplift in each year until we uplift the number of children required for that year.

### Boosted Sample

@@

sample_information <- function(int.dat, target.year) {
  hh_boosted <- int.dat %>%
    select(hidp, time, income_boosted, boost_amount, nkids) %>%
    filter(income_boosted == 'True') %>%
    group_by(time) %>%
    summarise(n_boosted = length(unique(hidp)),
              total_boost = sum(boost_amount),
              kids_boosted = sum(nkids))

  p1 <- ggplot(hh_boosted, aes(x = time, y = n_boosted)) +
    geom_line() +
    geom_vline(xintercept = target.year, linetype = 'dashed') +
    labs(title = 'Number of households receiving intervention') +
    xlab('Year') +
    ylab('Number Boosted')

  p2 <- ggplot(hh_boosted, aes(x = time, y = kids_boosted)) +
    geom_line() +
    geom_vline(xintercept = target.year, linetype = 'dashed') +
    labs(title = 'Number of children in households receiving intervention') +
    xlab('Year') +
    ylab('Number Children')

  p3 <- ggplot(hh_boosted, aes(x = time, y = total_boost)) +
    geom_line() +
    geom_vline(xintercept = target.year, linetype = 'dashed') +
    labs(title = 'Total boost amount') +
    xlab('Year') +
    ylab('Boost Amount')

@@

  p4 <- ggplot(mean.boost, aes(x = time, y = mean_boost)) +
    geom_line() +
    geom_vline(xintercept = target.year, linetype = 'dashed') +
    labs(title = 'Mean boost amount') +
    xlab('Year') +
    ylab('Boost Amount')

  print(p1)
  print(p2)
  print(p3)
  print(p4)
}

sample_information(int.dat, target.year = 2030)
```

@@

### SF_12_MCS

@@

#### Full Sample

@@

```{r}
full.sample.change.SF12 <- function(base.dat, int.dat) {
  base.all.SF12 <- base.dat %>%
    select(time, weight, SF_12) %>%
    group_by(time) %>%
    summarise(base.SF12 = weighted.mean(SF_12, w = weight))

@@

  ggplot(combined, aes(x = time, y = diff)) +
    geom_line() +
    geom_hline(yintercept = 0, linetype='dashed') +
    labs(title = 'Relative change in SF12') +
    xlab('Year') +
    ylab('Difference')
}

full.sample.change.SF12(base.dat, int.dat)
```

#### Families with children

@@

```{r}
all.families.change.SF12 <- function(base.dat, int.dat) {
  base.all.SF12 <- base.dat %>%
    select(time, weight, SF_12, nkids) %>%
    filter(nkids > 0) %>%
    group_by(time) %>%
    summarise(base.SF12 = weighted.mean(SF_12, w = weight))

@@

  ggplot(combined, aes(x = time, y = diff)) +
    geom_line() +
    geom_hline(yintercept = 0, linetype='dashed') +
    labs(title = 'Relative change in SF12') +
    xlab('Year') +
    ylab('Difference')
}
all.families.change.SF12(base.dat, int.dat)
```

#### Families w/ children under poverty line

@@

```{r}
poverty.families.change.SF12 <- function(base.dat, int.dat, threshold) {
  base.thresh <- merge(base.dat, threshold, by = 'time')
  int.thresh <- merge(int.dat, threshold, by = 'time')

@@

  ggplot(combined, aes(x = time, y = diff)) +
    geom_line() +
    geom_hline(yintercept = 0, linetype='dashed') +
    labs(title = 'Relative change in SF12') +
    xlab('Year') +
    ylab('Difference')
}

poverty.families.change.SF12(base.dat, int.dat, threshold)
```

@@

#### Treatment on the Treated

```{r}
treatment.on.treated.change.SF12 <- function(base.dat, int.dat) {
  boosted.byyear <- int.dat %>%
    filter(income_boosted == 'True')

  base.all.SF12 <- base.dat %>%
    select(time, weight, SF_12, nkids, pidp) %>%
    filter(pidp %in% boosted.byyear$pidp) %>%
    group_by(time) %>%
    summarise(base.SF12 = weighted.mean(SF_12, w = weight))

  int.all.SF12 <- int.dat %>%
    select(time, weight, SF_12, nkids, pidp) %>%
    filter(pidp %in% boosted.byyear$pidp) %>%
    group_by(time) %>%
    summarise(int.SF12 = weighted.mean(SF_12, w = weight))

@@

  ggplot(combined, aes(x = time, y = diff)) +
    geom_line() +
    geom_hline(yintercept = 0, linetype='dashed') +
    labs(title = 'Relative change in SF12') +
    xlab('Year') +
    ylab('Difference')
}

treatment.on.treated.change.SF12(base.dat, int.dat)
```

### True Treatment on Treated

Instead of looking at the difference in means

## Sustained Uplift

This intervention is similar to the random uplift intervention with one difference. In the first year that the intervention is applied, households are randomly chosen for uplift until the correct number of children for that year are uplifted. The difference comes in subsequent years. From year 2 onwards, households that have been previously intervened on will once again be uplifted to above the poverty line (if they are once again below). This is the meaning of the sustained intervention, where families are chosen at random and then maintained above the poverty line, instead of picking a random subset of households under the poverty line as in the random intervention.

### Boosted Sample

```{r}
sample_information(int2.dat, target.year = 2030)
```

### SF_12_MCS

#### Full Sample

```{r}
full.sample.change.SF12(base.dat, int2.dat)
```

#### Families with children

```{r}
all.families.change.SF12(base.dat, int.dat)
```

#### Families w/ children under poverty line

```{r}
poverty.families.change.SF12(base.dat, int.dat, threshold)
```

#### Treatment on the Treated

```{r}
treatment.on.treated.change.SF12(base.dat, int.dat)
```
